Report - Latest Rodent Data

### 2019-02-20 index.Rmd
updating with new function names

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
plot_cast()
```

@@

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
plot_species_casts()
```

@@

These figures are similar to the primary Total Abundance Forecast above, but for the abundance of three common rodent species. 
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
most_ab <- select_most_ab_spp()
for(i in 1:3){
  plot_cast(species = most_ab[i])
}
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
plot_cast_ts()
```

@@

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
plot_cast_point()
```

@@

These figures are similar to the primary Total Abundance Forecast above, but for the abundance of three common rodent species. 
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
most_ab <- select_most_ab_spp()
for(i in 1:3){
  plot_cast_ts(species = most_ab[i])
}
```

### 2019-02-20 report.Rmd
updating with new function names

Here's the most recent actual data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_species_casts(with_census = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_species_casts(with_census = TRUE, level = "All")
```

>>>>

Here's the most recent actual data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_cast_point(with_census = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_cast_point(with_census = TRUE, level = "All")
```
